DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-20 paper/main.tex
abstract revision

\begin{abstract}
We present DeepPicar, a low-cost deep neural network based
autonomous car platform. DeepPicar is a small scale
replication of a real self-driving car called DAVE-2 by NVIDIA. DAVE-2
drove on public roads using a deep convolutional neural network (CNN), 
which takes images from a front-facing camera as input and produces
car steering angles as output. DeepPicar uses the same 
network architecture---9 layers, 27 million connections and 250K
parameters---and can be trained to drive itself using a
web camera and a modest Raspberry Pi 3 quad-core platform in real-time.
Using DeepPicar, we analyze the Pi 3's computing capabilities to 
support end-to-end deep learning based real-time control of autonomous
vehicles. 
We also systematically compare other contemporary embedded
computing platforms using the DeepPicar's CNN based real-time control
workload.

We find all tested platforms, including the Pi 3, are capable of
supporting the CNN based real-time control, from 20 Hz up to 100
Hz depending on hardware platform. 
However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms; we observe
up to 11.6X control loop execution time increase due to such shared
resource contention. We evaluate state-of-the-art cache
partitioning and memory bandwidth throttling techniques on the Pi 3
in protecting the CNN workload. We find cache partition is
ineffective, while memory bandwidth throttling is an effective
solution.
\end{abstract}

>>>>

\begin{abstract}
We present DeepPicar, a low-cost deep neural network based
autonomous car platform. DeepPicar is a small scale
replication of a real self-driving car called DAVE-2 by NVIDIA. DAVE-2
uses a deep convolutional neural network (CNN), 
which takes images from a front-facing camera as input and produces
car steering angles as output. DeepPicar uses the same 
network architecture---9 layers, 27 million connections and 250K
parameters---and can drive itself in real-time using a web camera and
a Raspberry Pi 3 quad-core platform.
Using DeepPicar, we analyze the Pi 3's computing capabilities to 
support end-to-end deep learning based real-time control of autonomous
vehicles. 
We also systematically compare other contemporary embedded
computing platforms using the DeepPicar's CNN based real-time control
workload.

We find all tested platforms, including the Pi 3, are capable of
supporting the CNN based real-time control, from 20 Hz up to 100
Hz depending on hardware platform. 
However, we find that shared resource contention remains an
important issue that must be considered in applying CNN models on
shared memory based embedded computing platforms; we observe 
up to 11.6X execution time increase in the CNN based control loop due
to shared resource contention. To protect the CNN workload, we also
evaluate state-of-the-art cache partitioning and memory bandwidth
throttling techniques on the Pi 3. We find cache partition is
ineffective, while memory bandwidth throttling is an effective
solution.
\end{abstract}
